### 2021-06-17 paper/appendix_data.tex
Polish model summary.

    \floatfoot{\noindent
        \textit{Note:} Other contacts include all contacts that are not household
        members, school contacts or work contacts, for example leisure contacts or
        contacts during grocery shopping. The planned number of contacts is reduced by
        policies, seasonality and individual responses to events such as receiving a
        positive rapid test to the number of actual contacts with transmission potential.        % non recurrent
        In the model it is sampled every day which of the numbers of non recurrent
        contacts a person is planned to have. Note that the contact diaries include such
        high values that super spreading events are well possible in our model through
        non recurrent other models. We assume that individuals in households with
        children or teachers or retired individuals have additional non recurrent
        contacts during school vacations to cover things like family visits or travel
        during vacations. We estimate this to be on average 0.5 additional contacts per
        vacation day.
        % daily and weekly
        For the recurrent other contacts, individuals are assigned to groups that are
        time constant and that meet daily or weekly. The share of individuals that attend
        in a way that has transmission potential is reduced by policies, seasonality and
        individual responses to events such as receiving a positive rapid test. For
        weekly contacts, individuals are assigned to up to four groups that are time
        constant and that meet weekly. The day on which meetings take place varies
        between groups but stays the same for each group.
    }
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/work_recurrent_daily}
    \caption{Number of Daily Recurrent Work Contacts}
    \label{n_contacts_work_daily_recurrent}
    \floatfoot{\noindent Working individuals are assigned to groups that are time
        constant and that meet daily to match the given distribution of daily work contacts.
        You can think of these as for example colleagues with which one shares an office
        space. The share of individuals that attend in a way that has transmission potential
        is reduced by policies (such as a work from home mandate), seasonality and individual
        responses to events such as receiving a positive rapid test. Work contacts only take
        place between working individuals.}
\end{figure}

@@

All shares of individuals that would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.\comment[id=J]{Talk about the interpretation
of each line.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{\textbf{Share of Individuals that do a Rapid Test.}}
    \floatfoot{\noindent ...}
    \label{fig:rapid_test_demand}
\end{figure}

>>>>

    \floatfoot{\noindent
        \textit{Note:} Other contacts include all contacts that are not household
        members, school contacts or work contacts, for example leisure contacts or
        contacts during grocery shopping. The planned number of contacts is reduced by
        policies, seasonality and individual responses to events such as receiving a
        positive rapid test to the number of actual contacts with transmission potential.        % non recurrent
        In the model it is sampled every day which of the numbers of non recurrent
        contacts a person is planned to have. Note that the contact diaries include such
        high values that super spreading events are well possible in our model through
        non recurrent other models. We assume that individuals in households with
        children or teachers or retired individuals have additional non recurrent
        contacts during school vacations to cover things like family visits or travel
        during vacations. We estimate this to be on average 0.5 additional contacts per
        vacation day.
        % daily and weekly
        For the recurrent other contacts, individuals are assigned to groups that are
        time constant and that meet daily or weekly. The share of individuals who attend
        in a way that has transmission potential is reduced by policies, seasonality and
        individual responses to events such as receiving a positive rapid test. For
        weekly contacts, individuals are assigned to up to four groups that are time
        constant and that meet weekly. The day on which meetings take place varies
        between groups but stays the same for each group.
    }
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/distributions_of_the_number_of_contacts/work_recurrent_daily}
    \caption{Number of Daily Recurrent Work Contacts}
    \label{n_contacts_work_daily_recurrent}
    \floatfoot{\noindent Working individuals are assigned to groups that are time
        constant and that meet daily to match the given distribution of daily work contacts.
        You can think of these as for example colleagues with which one shares an office
        space. The share of individuals who attend in a way that has transmission potential
        is reduced by policies (such as a work from home mandate), seasonality and individual
        responses to events such as receiving a positive rapid test. Work contacts only take
        place between working individuals.}
\end{figure}

@@

All shares of individuals who would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.\comment[id=J]{Talk about the interpretation
of each line.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{\textbf{Share of individuals who do a Rapid Test.}}
    \floatfoot{\noindent ...}
    \label{fig:rapid_test_demand}
\end{figure}
